---
title: "EDA_FinalProject"
author: "Ehsan Ebrahimian"
date: "6/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## PART 1
###  Finding Number of Rivers per Country
###  Finding Number of Stations per Country
###  Finding Number of Stations per River


_Loading needed Libraries and Files:_

```{r}
library(data.table)
library(mapview)
library(plyr)
library(sf)
library(ggplot2)
runoff_eu_day <- readRDS('data/runoff_eu_day.rds')
runoff_eu_info <- readRDS('data/runoff_eu_info.rds')

```



_Numbe of Countries in Record_

```{r}
stations_country <- as.data.frame(table(runoff_eu_info[, .(Station), by = Country]))
length(unique(stations_country[,"Country"])) 
```

_Number of Stations per Country_
  
```{r}
stations_per_country <- ddply(stations_country, "Country", numcolwise(sum))
stations_per_country
sum(stations_per_country[,2])
```

_Distribution of Stations on Map_
```{r}  
map_of_stations <- st_as_sf(runoff_eu_info,coords = c('Lon', 'Lat'),crs = 4200)
mapview(map_of_stations, map.types = 'Stamen.Watercolor')
```
 
 As it can be seen on the map, Many stations are in Central Europe, and Northern Europe. There is a lack of data of rivers in Southern Europe. 
Germany has the largest number of stations with 78 stations (DE),and Finland, Norway, Czechia and Sweden have more than 20 stations each.

_Number of Rivers per Country_
```{r}
rivers_per_country <- runoff_eu_info[, list(River, Country)]
rivers_per_country <- rivers_per_country[!duplicated(rivers_per_country$River)]
rivers_per_country <- rivers_per_country[, .N, by = Country]
rivers_per_country
```


_And, This is Total number of rivers:_
```{r}
sum(rivers_per_country[,2])
```


_Number of stations per River_
```{r}
stations_per_river <- runoff_eu_info[, list(Station, River)]
stations_per_river <- stations_per_river[, .N, by = River]
stations_per_river
sum(stations_per_river[,2])

```
 DANUBE  -  RHINE   -  KOKEMAENJOKI  - ELBE  - WESSER  (rivers with highest numbers of stations)
   
   _Distribution of Stations according to Height (Alt)_
```{r}
distribution <- runoff_eu_info[, list(Station, Lat, Lon, Alt)]


year <- runoff_eu_info[, list(Station, N.Years)]
year
ggplot(data = distribution, aes(x = Lat, y = Lon, size = Alt)) +
  geom_point()
 
```

_Time Distribution of Records_
```{r}
ggplot(data = year, aes(x = 1:208, y = N.Years)) +
  geom_line(colour='red') +
  geom_point(colour='purple') +
  geom_smooth(method = "lm")

mean(year$N.Years)
```


 Averagely there are 101 years of data for each station.

[Next Page ->](https://rpubs.com/e_ebrahimian/eda_fp_2)


